The Suburbanisation of Poverty in Scotland’s Cities: Urban Regeneration or

### 2016-10-28 markdown/draft.RmD
make slight edit to markdown draft

* In all four of Scotland’s major cities, poverty has become more suburbanized over the last 12 years. The proportion of poor or ‘income deprived’ people in inner city areas fell, while the number of non-poor people in these areas rose.
*	The latest data, published as part of the Scottish Index of Multiple Deprivation today, confirm this trend, albeit with some variation between cities. The process is advancing most in Edinburgh with Glasgow second. It is slowest in Dundee.
*	The central areas of all four cities retained their share of the total city population or saw this rise between 2004 and 2016. This is a significant change from decades of population losses and is generally to be welcomed from an environmental point of view. It suggests that planning policies have succeeded in encouraging people to live in higher-density locations which tend to be better served by public transport, reducing reliance on cars. 
*	However the displacement of lower income groups suggests these policies will fail to deliver the socially mixed communities which planners have so frequently advocated as part of their vision for sustainable cities. 
*	The main reason for this change is likely to be the continued reductions in housing subsidies for lower income households. The last 20 years have seen the loss of social rented housing and greater reliance on private renting, combined with the reductions in housing benefits. As a result, inner city locations appear to be increasingly beyond the reach of poorer households.

>>>>

* In all four of Scotland’s major cities, poverty has become more suburbanized over the last 12 years. The proportion of poor or ‘income deprived’ people in inner city areas fell, while the number of non-poor people in these areas rose.
*	The latest data, published as part of the Scottish Index of Multiple Deprivation (SIMD) on 31 August 2016, confirm this trend, albeit with some variation between cities. The process is advancing most in Edinburgh with Glasgow second. It is slowest in Dundee.
*	The central areas of all four cities retained their share of the total city population or saw this rise between 2004 and 2016. This is a significant change from decades of population losses and is generally to be welcomed from an environmental point of view. It suggests that planning policies have succeeded in encouraging people to live in higher-density locations which tend to be better served by public transport, reducing reliance on cars. 
*	However the displacement of lower income groups suggests these policies will fail to deliver the socially mixed communities which planners have so frequently advocated as part of their vision for sustainable cities. 
*	The main reason for this change is likely to be the continued reductions in housing subsidies for lower income households. The last 20 years have seen the loss of social rented housing and greater reliance on private renting, combined with the reductions in housing benefits. As a result, inner city locations appear to be increasingly beyond the reach of poorer households.
